Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-02-19 PaperVictor.tex
Minor changes, including removal of useless spaces

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}

%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}

@@

	\author[1,2,3]{V. Castillo-Gallardo}
	\cormark[1]
	\ead{ing.victorcg@gmail.com}
	\credit{Conceptualization, Software $\&$ Investigation, synthesis $\&$ characterization, Writing}
	\address[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
		Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
		Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
		M\'{e}xico.}

	\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
	\ead{fmatpuente@gmail.com}
	\credit{Software $\&$ Investigation}
	\address[2]{Instituto de Ciencias F\'{i}sicas, Universidad
		Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
		Col. Chamilpa, 62210 Cuernavaca, Morelos, M\'{e}xico.}
	\address[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
		Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
		Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}

@@

	\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
	\ead{hiperezag@yahoo.com}
	\credit{Investigation and Supervision}

	\author[2]{W. Luis Moch\'{a}n}
	\ead{mochan@fis.unam.mx}
	\credit{Conceptualization, Funding acquisition, Investigation, Supervision, Writing - review $\&$ editing}

	\author[1]{V Agarwal}
	\cormark[2]
	\fnmark[1]
	\ead{vagarwal@uaem.mx}
	\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}

	\cortext[cor1]{Corresponding author}
	\cortext[cor2]{Principal corresponding author}
	\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM}

@@

	\section{Introduction}
	Photonic crystal (PC)-based structures have been extensively investigated due
	to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
	Photons entering a PC interact with its periodically varying dielectric constant and
	their energies are consequently organized into photonic bands. In
	analogy to electronic bands withiny a
	crystal, propagation is forbidden if the energy lies
	within certain regions known as photonic band gaps (PBG's). Thus, the
	PC behaves as a mirror if illuminated by light with frequencies
	within in a PBG. For several applications it is useful to fabricate
	{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
	The use of metallic
	mirrors is limited due to their relatively large absorption at the
	visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
	consists of low-absorption dielectric
	structures,  which may be designed for specific frequency
	ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
	applications in optoelectronics, optical telecommunications and computing,
	laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
	\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
	of periodically alternating
	layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
	corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
	thicknesses corresponds to a quarter of a wavelength
	$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
	wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
	which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
	and the number of periods are large enough. Mirrors with high
	reflectance within a wider frequency range may be engineered by
	using different nominal wavelengths for different layers.
	One way to obtain such structures is to gradually change the width of
	the layers as a function of their depth, producing
	\textit{chirped}-type structures \cite{Zipock1997}.
	Another alternative is to stack BMs, in such a way that their reflection bands partially
	overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

>>>>

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}

@@

\author[1,2,3]{V. Castillo-Gallardo}[orcid=0000-0002-8157-3534]
\cormark[1]
\ead{ing.victorcg@gmail.com}
\credit{Conceptualization, Software \& Investigation, synthesis \& characterization, Writing}
\address[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
  Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
  Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
  M\'{e}xico.}

\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}[orcid=0000-0003-3719-8535]
\ead{fmatpuente@gmail.com}
\credit{Conceptualization, Software $\&$ Investigation}
\address[2]{Instituto de Ciencias F\'{i}sicas, Universidad
  Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
  Col. Chamilpa, 62210 Cuernavaca, Morelos, M\'{e}xico.}
\address[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
  Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
  Francisco J. M\'ugica S/N 58030, Morelia, Mich., M\'{e}xico.}

@@

\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}[orcid=0000-0002-8572-1485]
\ead{hiperezag@yahoo.com}
\credit{Investigation and Supervision}

\author[2]{W. Luis Moch\'{a}n}[orcid=0000-0003-0418-5375]
\ead{mochan@fis.unam.mx}
\credit{Conceptualization, Funding acquisition, Investigation, Supervision, Writing - review $\&$ editing}

\author[1]{V Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM}

@@

\section{Introduction}

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands withiny a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.
